%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{ -0.5in}
\addtolength{\evensidemargin}{ -0.5in}
\addtolength{\textwidth}{ 1in}
\addtolength{\topmargin}{ -.5in}
\addtolength{\textheight}{ 1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Daniel J Barton} \\ \vspace{1pt}
    \small (+1) 763-333-6834 $|$ \href{mailto:Daniel.Barton446@gmail.com}{\underline{Daniel.Barton446@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/daniel-barton-36a360204/}{\underline{linkedin.com/Daniel-Barton}} $|$
    \href{https://github.com/DanielBarton446}{\underline{github.com/DanielBarton446}}
\end{center}

%------OBJECTIVE STATEMENT------
\section{Objective}
Seeking to leverage concepts from the SOLID principle to operational observability and automation systems.
Maintainability and extensibility are often sacrificed to yield quick results. I prioritize sustainable solutions.

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Support Engineer -- Metadata Frameworks}{ November 2023 -- Present}
      {Susquehanna International Group}{ Bala Cynwyd, Pennsylvania}
    \resumeItemListStart
      \resumeItem{ Lead a major migration task for on-prem infrastructure for minimized impacts on trading operations for the Firm}
      \resumeItem{ Improved several manual operational tasks with automation where allowed, and through data representation otherwise. One particular case cut down a low priority daily task from hours to minutes. }
      \resumeItem{ Implemented automatic token bundling for application deployment with our in-house deployment tooling}
      \resumeItem{ Implemented multiple python-based monitoring additions. One gap was alerting on silently failing ELK watchers}
    \resumeItemListEnd

    \resumeSubheading
      {Reliability Engineer -- Observability}{ May 2022 --- November 2023}
      {Bestbuy}{ Richfield, Minnesota}
      \resumeItemListStart
        \resumeItem{Maintained and enhanced observability tooling: Splunk, Elastic, Grafana, Graphite}
        \resumeItem{Frequently worked with Terraform, Chef, and Ansible to provision and configure AWS infrastructure}
        \resumeItem{Automated snapshot cleanup for Grafana, alongside building an improved restoration mechanism for dashboards}
        \resumeItem{Lead the migration task for authentication from crowd auth over to AD through SAML for Splunk}
        \resumeItem{Implemented automation for Splunk index creation. This enabled app teams to not be reliant on the regular 2-week deployment cycle where they would need to create a ticket to be added to the queue of new indexes}
        \resumeItem{Re-architect log file backup mechanism (for resiliency) for tens of thousands of dollars in yearly cost savings}
      \resumeItemListEnd

    \resumeSubheading
      {Quality Intern at Boston Scientific}{June 2021 --- September 2021}
      {Boston Scientific}{ Arden Hills, Minnesota}
      \resumeItemListStart
        \resumeItem{Self-led the design and implementation to streamline diagnostics of Latitude Communicators. Circa 80\% of communicators returned were targetable for this product. This saved around 8 hours a week for technicians}
        \resumeItem{Utilized Tera-Term macro programming language to implement automated testing}
        \resumeItem{Finished development a month ahead of schedule, spending the remaining time to manually validate and create thorough documentation regarding the new testing product} 
      \resumeItemListEnd
     
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Minnesota}{ Minneapolis, Minnesota}
      {Bachelor of Computer Science}{ May 2022}
          \resumeItemListStart
            \resumeItem{GPA: 3.38}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{[Python] Optical Digit Classifier Neural Network} $|$ \emph{Numpy}}{November 2021}
          \resumeItemListStart
            \resumeItem{Built a multi layer perceptron to recognize pre-processed images of handwritten numbers. Determined ideal number of hidden units within the hidden layer for optimal recognition accuracy and run-time. Test accuracy was 93\%.  2D and 3D visualization using the hidden units with the largest variance to show the distribution of classifications.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{[C] Basic Chatroom} $|$ \emph{Pthread}}{April 2021}
          \resumeItemListStart
            \resumeItem{Local server-client relationship from scratch allowing for chatting utilizing FIFO’s. Extendable to sockets and over-the-network chatting. Utilized elementary multi-threading, and taught elementary concepts of networking.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{[C++] Voting System Simluation} $|$ \emph{doxygen}}{April 2022}
          \resumeItemListStart
            \resumeItem{School team project that acted as a demonstration of waterfall and agile scrum work methodologies}
            \resumeItem{Created central waterfall documents, SRS and SDD}
            \resumeItem{Simulated user stories with arbitrary feature requests to be implemented within 72 hours on an existing codebase}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:}{ Python, C, C++, Rust, MySQL, Node.js, JavaScript, HTML, CSS} \\
     \textbf{Technologies:}{ AWS, Openshift, Terraform, Chef, Ansible} \\
     \textbf{Certifications:}{ Backend Development and API -- FreeCodeCamp} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
